scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Suggest other IDEs also. Notes about notebooks

While several interpreters are available to execute interactively Python
instructions and scripts, the most popular one in the scientific world is
the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates for example a debugger,
introspection and profiling methods, and online help. Several IDEs
(Integrated Development Environment) integrate the IPython interpreter,
together with other components such as a text editor. For example, Spyder 
is a popular IDE (see Fig.~\ref{fig:spyder}).

@@

The Jupyter notebook~\citep{Kluyver2016} is a web application which has
grown from the IPython project, although the two projects have now
diverged. Jupyter notebooks provide an interactive development
environment within an Internet browser, where live code can be enriched
by explanatory text, equations and visualizations (figure or not??).

>>>>

While several interpreters are available to execute interactively Python
instructions and scripts, the most popular one in the scientific world is
the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates syntax highlighting, text auto-completion,
a debugger,
introspection and profiling methods, and online help. Several
Integrated Development Environments (IDEs) include IPython,
together with other components such as a text editor. Notable examples
include Spyder (Fig.~\ref{fig:spyder}), PyCharm, and Visual Studio Code.

@@

The Jupyter notebook~\citep{Kluyver2016} is a web application that grew
from the IPython project. Jupyter notebooks provide an interactive development
environment within a web browser, where live code can be enriched
by explanatory text, equations and visualizations (FIGURE).
(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)
